\section*{ \begin{center}
ABSTRACT
\end{center} }

\vspace{0.4cm}

\noindent
The contemporary academic university environment forces students to process an exponential volume of unstructured technical data, triggering severe cognitive overload and isolating learning efforts. To mitigate these deficiencies, this research evaluates the empirical impact of the digital ecosystem SynapTome on students' academic performance, retention, and collaborative workflows. Methodologically, the platform integrates an adaptive handwritten text recognition (HTR) pipeline based on the TrOCR Transformer architecture subjected to specific fine-tuning, a factual Retrieval-Augmented Generation (RAG) middleware coupled with Large Language Models (LLMs), and an indexed relational-vector Knowledge Graph topology synced in real-time via SignalR. 

\vspace{0.3cm}

\noindent
The field results demonstrated a drastic paradigm shift for the students. The optimized TrOCR pipeline reduced the character error rate (CER) in complex scientific notation from an initial 34.20\% using traditional OCR tools to a stable 4.15\%, preventing technical information loss. Furthermore, the RAG middleware restricted the semantic inference space to the verified academic corpus, mitigating LLM hallucinations to an asymptotic 1.20\%. This factual alignment lifted average midterm exam scores from a marginal 11.80 to an outstanding 15.90. Finally, automated spaced-repetition quizzes combined with topological interconnections optimized cognitive processes, reducing subjective academic stress by 46.30 points on the NASA-TLX scale and ensuring long-term knowledge retention above 93.50\%. Statistical validation via a right-tailed Student's t-test ($t = 3.21 > t_{\text{critical}} = 2.92$) rejected the null hypothesis with a 95\% confidence level, concluding that the implementation of the SynapTome intelligent ecosystem significantly optimizes learning management, precision digitalization, and collective intelligence execution among university students compared to traditional isolated methods.

\vspace{0.6cm}

\noindent
\textbf{Keywords:} Knowledge Management Ecosystem, Retrieval-Augmented Generation (RAG), TrOCR Transformer, Knowledge Graphs, Collective Intelligence, Cognitive Overload Mitigation.